Investigating the influence of genre preferences on movie/series rating patterns

### 2024-03-22 gen/paper/paper.Rmd

In this paper we investigate consumers’ movie and series preferences
using four of IMDb's datasets containing movie data. First, these
datasets are loaded, inspected, merged and cleaned. Next, the
data is analyzed using a regression analysis. This regression analysis
regresses all movie and series genres against the average ratings over
a period of 5 years. Additionally, the variables title, movieType and
time are used as control variables to improve the interpretability of
the estimates.

| Name of Variable | Contents of Variable                                                                                                                                             | Used as .. in Analysis |
|------------------|------------------------------------------------------------------------------------------------------------------------------------------------------------------|------------------------|
| Average Rating   | The average rating on IMBd per title of a given movie or series.                                                                                                 | Dependent Variable     |
| Genre Types      | Genre Types is a cluster for all 26 genre dummies that contain the value 1 if the movie or series contains that genre and otherwise 0.                           | Independent Variable   |
| titleType        | This variable indicates whether a title is a movie or a series.                                                                                                  | Fixed Effect           |
| Title            | The title is the given title of any unique movie or series                                                                                                       | Fixed Effect           |
| 5 Year Window    | The 5 year windown (or ' slide_window_5' indicates between what 5 year window a movie or series belongs to. For example a movie from 2003 belonging to 2000-2004 | Split Varible          |

### Average Movie Rating

>>>>

In this paper we investigate consumers’ movie and series preferences
using four of IMDb's datasets containing movie data. First, these

datasets are loaded, cleaned, inspected, merged and cleaned. Next, the
data is analyzed using a regression analysis. This regression analysis
regresses all movie and series genre's against the average rating's over
a sliding period of 5 years. Additionally, the variables title,
movieType and time are used as control variables to improve the
interpret ability of the estimates.

| Name of Variable | Contents of Variable                                                                                                                                             | Used as .. in Analysis |
|------------|-------------------------------------------------|------------|
| Average Rating   | The average rating on IMBd per title of a given movie or series.                                                                                                 | Dependent Variable     |
| Genre Types      | Genre Types is a cluster for all 26 genre dummies that contain the value 1 if the movie or series contains that genre and otherwise 0.                           | Independent Variable   |
| titleType        | This variable indicates whether a title is a movie or a series.                                                                                                  | Fixed Effect           |
| Title            | The title is the given title of any unique movie or series                                                                                                       | Fixed Effect           |
| 5 Year Window    | The 5 year windown (or ' slide_window_5' indicates between what 5 year window a movie or series belongs to. For example a movie from 2003 belonging to 2000-2004 | Split Varible          |

### Outcome Variable: Average Movie Rating
